---
title: "Assignment 03"
author: "Sean Kim"
format:
  html:
    embed-resources: true
---

```{}
```

```{r}

library(tidytext)
library(dplyr)
library(ggplot2)

url <- "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/03_pubmed/pubmed.csv"
data <- read.csv(url)

#tokenize and count
word_freq <- data %>%
  unnest_tokens(word, abstract) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)

#10 most frq words
head(word_freq, 10)
```

2.  Bigrams:

    ```{r}
    top_bigrams <- data %>%
      unnest_tokens(bigram, abstract, token = "ngrams", n = 2) %>%
      count(bigram, sort = TRUE) %>%
      head(10)

    #Visualize
    ggplot(top_bigrams, aes(x = reorder(bigram, n), y = n)) +
      geom_bar(stat = "identity") +
      labs(x = "Bigram", y = "Frequency", title = "Top 10 Bigrams") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    ```

```{r}
top_tfidf_tokens <- data %>%
  unnest_tokens(word, abstract) %>%
  anti_join(stop_words) %>%
  count(word, term) %>%
  bind_tf_idf(word, term, n) %>%
  group_by(term) %>%
  slice_max(tf_idf, n = 5) %>%
  ungroup() %>%
  arrange(term, desc(tf_idf))

print(top_tfidf_tokens)
```

Compared to question 1, these results are quite different, giving much more information. Covid was most often associated with "19" in the first, whereas this query gives us "pandemic, coronavirus, sars" - giving us more information about the nature of covid as a respiratory syndrome and a coronavirus. For another example, we get a clue that preeclampsia is associated with pregnancy using this method of searching. This was not apparent in the results of question 1.
